Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-04-28 literature/paper_draft.Rmd
cleanup

For forecast errors $\hat{e}_{t|t-1}$, the unbiased sample covariance of in-sample one-step-ahead base forecast errors is: $$
\hat{W}_1 = \frac{1}{T} \sum_{t=1}^{T} \hat{e}_{t|t-1} \hat{e}_{t|t-1}^{\top}.
$$

@@

>>>>

For forecast errors $\hat{e}_{t|t-1}$, the unbiased sample covariance of in-sample one-step-ahead base forecast errors is:

$$
\hat{W}_1 = \frac{1}{T} \sum_{t=1}^{T} \hat{e}_{t|t-1} \hat{e}_{t|t-1}^{\top}.
$$

@@

where $\hat{r}_{ij}$ is the $ij$th element of $\hat{\boldsymbol{R}}_1$, the 1-step-ahead sample correlation matrix (obtained from $\hat{\boldsymbol{W}}_1$) to shrink it toward an identity matrix

### 2025-04-28 research_proposal/research_proposal.qmd
cleanup

![Diagram of 2-level hierarchical tree structure](D:/Github/Recon_Honours_Thesis/research_proposal/figs/hierarchical_structure.png){width="40%"}

@@

The example summing matrix $\boldsymbol{S}$ for the tree structure in *Figure 1* is:

@@

If we use equation @eq-1 to forecast the time series, we would not be utilising all the information in the data, since we only forecast the bottom-level series $\boldsymbol{b}_t$ then aggregate to the higher-level. Thus, Hyndman et al. (2011) showed that existing methods could be expressed as:

@@

Wickramasuriya et al. (2019) reframed the problem by taking an optimisation approach rather than the regression. They formulated the problem as minimising the variances of all reconciled forecasts from equation @eq-2, which happens to be equivalent to the trace of the covariance matrix (sum of the diagonal elements). This is known as the Minimum Trace (MinT) reconciliation method. The MinT solution is given by $G_h = (S'W_h^{-1}S)^{-1}S'W_h^{-1}$, and $W_h$ is the covariance matrix of the h-step-ahead base forecast errors.

>>>>

![Diagram of 2-level hierarchical tree structure](D:/Github/Recon_Honours_Thesis/research_proposal/figs/hierarchical_structure.png){#fig-hierarchy width="40%"}

@@

The example summing matrix $\boldsymbol{S}$ for the tree structure in @fig-hierarchy is:

@@

If we use @eq-1 to forecast the time series, we would not be utilising all the information in the data, since we only forecast the bottom-level series $\boldsymbol{b}_t$ then aggregate to the higher-level. Thus, Hyndman et al. (2011) showed that existing methods could be expressed as:

@@

Wickramasuriya et al. (2019) reframed the problem by taking an optimisation approach rather than the regression. They formulated the problem as minimising the variances of all reconciled forecasts from @eq-2, which happens to be equivalent to the trace of the covariance matrix (sum of the diagonal elements). This is known as the Minimum Trace (MinT) reconciliation method. The MinT solution is given by
